Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, and the WEAI Conference}

### 2021-11-04 latex/paper/Spillover.tex
Finished Revising Paper

Using this potential outcome framework, I define the different possible treatment/spillover effects of interest and the relative advantage and interpretation of each. First, there is the `switching effect' which is the relevant parameter for local policy makers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units''. It is difficult to estimate the switching effect without parametric assumptions. The reason for this is that the magnitude of the switching effect potentially depends on the treatment status of a unit's neighbors. For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities versus the case where a close neighbor already has constructed one. Therefore, switching effects are defined seperately for each level of exposure and estimation of a switching effect requires knowledge of which units experience the same level of exposure. While the switching effect is not identified nonparametrically in general, there is one effect that is identified under mild assumptions. This effect is the `direct effect' of treatment which represents the switching effect for units with zero exposure to other treatment. That is, what are the effects of turning on a unit's treatment if this were the \emph{only} unit to be treated in their area.

Second, there is the `total effect' which is the relevant parameter for national policy makers who want to answer ``What is the average effect of implementing the entire treatment regime?''. This treatment effect summarizes what were the effects of going from the world with no treatment to the entire vector of treatment status. I further show that this effect comes from two sources: the direct effect and the average spillover effect from other treated units.

The standard difference-in-differences estimate identifies none of these treatment effects in the presence of spillovers. The first result of the paper shows that the difference-in-differences esitmand can be decomposed into the direct effect plus two additional bias terms resulting from the spillovers. The intuition is as follows. First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend. When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated units' change in outcomes. In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect. For example, if nearby control units also benefit from treatment, then researchers would underestimate the positive benefits of treatment. Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. The spillover onto other treated units is averaged into the treated units' change in outcomes. Therefore the bias of treatment effect is the same sign as the sign of the spillover. Last, since the total effect is the direct effect plus the average spillover effect on treated units, the difference-in-differences estimand can also be decomposed into the total effect minus the average spillover effect on control units.

This paper then defines conditions under which each treatment effect is nonparametrically identified. I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences of treatment which requires \emph{either} parametrization of spillovers \emph{or} under certain constraints on the spillover effects. The other two treatment effects considered are able to be identfified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature which holds in the case where spillover effects are only experienced by units close to treated units. This could fail in the case of general equilibrium shocks that cause units far away to be affected by treatment.

Under the assumption that spillovers are local, I show a common adjustment of including an indicator for being affected by spillovers will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers. In my decomposition of the treatment effect estimate, the bias terms are the \textit{average} spillover effects onto treated and control units. An indicator variable interacted with treatment status therefore can estimate these two averages and remove them from the difference-in-differences estimate. Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space. The only assumption required is selecting the maximum distance from treated units spillovers can occur.\footnote{Even if the maximum distance is not large enough, since treatment effects typically decay over distance, most of the bias will still be removed. Including too many units in the indicator will increase the variance in the estimates for average spillover effects as the other control units identify the parallel counterfactual unit.}

The modified difference-in-differences framework with an added spillover indicator provides a theoretically poor estimate of spillover effects as it averages over all units with the indicator equal to 1 which can include units that are unaffected by spillovers. The above method can be improved by creating a set of distance bins from treated units (e.g. being 0-20 miles, 20-40 miles, 40-60 miles from treated unit) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers. In some cases, the bins can be determined in a data driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single large indicator, this estimator still consistently estimates the treatment effect of interest. This estimator has the added benefit that each indicator will estimate the average spillover effect on treated/control units within that distance range which provides a more complete picture of which units are affected by treatment and at what magnitude.

@@

I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}. I contribute to this literature in two ways. My paper is the first to consider identification in terms of general potential outcomes. Other papers derive results for specific spillover mappings and if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs. Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.

This paper relates to a literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work. See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.} Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings.

Partial inference allows interference between but not across groups.. \citep{Hudgens_Halloran_2008,Vazquez-Bare_2019}. This allows for seperate identification of treatment and spillover effect in experimental settings. My paper ...

\citet{Savje_Aronow_Hudgens_2021} show what is identified under no assumptions of interference. My paper shows under a different set of assumptions what is estimated and how to estimate effects seperately ...

There is a large literature on estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers. Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares units in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects. This allows standard difference-in-differences estimation of both the direct effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters).

There is a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster by using a potential outcomes framework. \citet{Vazquez-Bare_2019} presents a potential outcomes model that explicitly accounts for ``within-group'' spillovers in experiments which allows for seperate estimation of direct effect and spillover effects by a simple differences-in-means. I extend this work by focusing on difference-in-differences estimation in non-experimental settings. \citet{Savje_Aronow_Hudgens_2021} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects. My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers. These estimates can be combined to estimate their definition of average treatment effect. The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.

I also contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}. I contribute to this literature in two ways. First, my paper derives an explicit form for this bias in terms of general potential outcomes which allows my results to capture many different forms of spillovers. For the above papers, if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs if they have one derived explicitly. Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.

@@

This section will present a potential outcome framework that formalizes spatial spillovers. Following the canonical difference-in-differences framework, I observe a panel of units for periods $t \in \{0,1\}$ and treatment turns on between periods for some of the units.\footnote{This can be extended to multiple periods by replacing $Y_{i0}$ and $Y_{i1}$ throughout with pre- and post- sample averages of $Y_{it}$. This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Let $D_{i}$ be an indicator equal to one if unit $i$ is treated and therefore treatment status is defined as $D_{it} = D_{i} * \one(t = 1)$.

@@

Potential outcomes, denoted $Y_{it}(D_i, h(\vec{D},i))$, are a function of unit $i$'s own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments. The non-negative scalar- or vector-valued function $h(\vec{D}, i)$ is referred to as an `exposure mapping'. This setup follows \citet{Vazquez-Bare_2019} who studies identification of spillover effects under an experimental setting.\footnote{Note that throughout, expectations and inference are conditional on the vector of exposure mappings. In design-based settings, the distribution of exposure mappings is known so expectations can be taken without conditioning on the vector of exposure mappings. See \citet{Savje_Aronow_Hudgens_2021} for discussion estimation and inference when the treatment design is known.}

The exposure mapping measures the intensity at which unit $i$ is affected by spillovers. Without restrictions on the exposure mapping, nonparametric identification of treatment effects will be impossible. The main assumption for identification, as will be formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = \vec{0}$ . In the world of no spillovers, that is $h(\vec{D}, i) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status. The exposure mapping formalizes the SUTVA violation by summarizing how outcomes are affected by other unit's treatment assignment.

@@

\begin{example}
    $h(\vec{D}, i)$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure which tells the distance unit $i$ is from unit $j$.  In this case \begin{equation}\label{eq:h_within}
        h(\vec{D}, i) = \max_{j \neq i} D_j * \one[ d(i,j) < \bar{d} ] 
    \end{equation}
    This exposure mapping is a realistic specification when it is assumed that spillover effects do not decay over distance until $\bar{d}$ and the intensity of spillovers does not depend on the number of neighboring units treated. For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}. In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library. The benefits of access to a neighboring town library does not depend on whether people can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.  
\end{example}

\begin{example}
    Second, $h(\vec{D}, i)$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
        h(\vec{D}, i) = \sum_{j \neq i} D_j * \one[ d(i,j) < \bar{d} ].
    \end{equation}
    This exposure mapping is no longer binary, so the intensity of spillovers is additive in the number of nearby units treated. In the context of wholesale store openings, this exposure mapping captures the additive nature of agglomeration economies. As more nearby counties receive new stores, the force of agglomeration and therefore the spillover effect increases (e.g. \citet{Basker_2005}).
\end{example}

\begin{example}
    Last, $h(\vec{D}, i)$ is a spatial decay function where exposure decreases with distance. In this case, spillover intensity is the sum across all treated observations' decay term, i.e. \begin{equation}\label{eq:h_decay}
        h(\vec{D}, i) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
    \end{equation} 
    This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units. This creates problems with inference because it implies potential correlation between all units' error terms. For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed that spillover effects decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using a non-linear least squares routine. In the literature on R\&D investment, for example, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure. This specification features exponential decay over distance which captures the theoretical insight that research spending in closer locations has a larger effect than further away spending.
\end{example}

@@

In setups without spillovers, treatment effects for an individual unit is well defined as $\tau_i \equiv Y_{i1}(1) - Y_{i1}(0)$, i.e. the effect of turning on treatment for a unit and the above two assumptions would lead to identification of the average effect by the traditional difference-in-differences estimator. In the presence of spillovers, there are multiple treatment effects that can be defined in this setting. This subsection will define them and discuss their relative advantages/disadvantages.

The natural analogue to the above treatment effect which I will label the `switching effect' is:
\[
    \tau_{i, switch}(h(\vec{D}, i)) \equiv Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i)).
\] 
This is the effect of changing only unit $i$'s treatment status while keeping their exposure to spillovers constant. This treatment effect is policy relevant as it summarizes what would happen if a `local' policy makers decide to enact the policy for unit $i$ (implicity keeping $h$ constant). It is important to note that the switching effect can depend on the level of exposure. For instance, consider the construction of libraries in towns. The effect of library construction in a town that is far away from any other library ($h = \vec{0}$) can be different than a town that is very close to a neighboring town's library (large exposure), hence the dependence of $\tau_{i, switch}$ on $h(\vec{D},i)$. Since the size of the switching effect depends on a units exposure level, we will consider an average switching effect at each value of exposure, 
\[
    \tau_{\text{switch}}(\vec{h}) \equiv \condexpec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i))}{D_i = 1, h(\vec{D}, i) = h}.
\]

% Work by \citet{Savje_Aronow_Hudgens_2021} suggests averaging the switching effect over exposure levels,
%\[ 
%    \tau_{\text{avg,switch}} \equiv \expec{\tau_{i, switch}(h(\vec{D},i)) \vert D_i = 1}.
%\] 
%This estimand averages the switching effect over all treated units and hence average over the distribution of exposure. Any given unit $i$ trying to understand the effect of switching on a policy can't use this parameter as it averages over exposures different than theirs. More, this parameter can not be identified without further assumptions as the distribution of exposure mappings is not necessarily the same for control units as treated units.\footnote{\citet{Savje_Aronow_Hudgens_2021} discuss conditions on the distribution of exposure mappings that can lead to asymptotic identification of the average switching effect. However it relies on design-based assumptions that do not apply here.}

There is a particular switching effect at zero exposure that I call the `direct effect' of treatment, 
\[
    \tau_{\text{direct}} \equiv \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, h(\vec{D},i) = \vec{0}} = \tau_{\text{switch}}(\vec{0}),
\] 
which measures the average effect of being treated \emph{among unexposed treated units}. Specifying this particular switching effect will prove useful when discussing identification as it requires fewer assumptions than switching effects at other exposure levels. As discussed above, this is not necessarily a policy-relevant parameter for every unit if the switching effect has different magnitudes at different levels of exposure.

The second policy-relevant parameter is the `total effect of treatment': 
\[
    \tau_{\text{total}} \equiv \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}.
\] 
As opposed to the switching effect, which keeps exposure constant, the total effect looks at turning on treatment \emph{and} going from zero exposure to $h(\vec{D}, i)$ simultaneously. This can be thought of as going from the world with a \emph{complete} absence of treatment, $\vec{0}$ to the current treatment vector $\vec{D}$. This treatment effect is helpful for `national' policy makers in order to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.

To better understand how the above treatment effects are connected, it will be useful to formalize a unit's `spillover effect' as:
\[
    \tau_{i, \text{spill}}(D_i, h(\vec{D},i)) \equiv Y_{i1}(D_i, h(\vec{D}, i)) - Y_{i1}(D_i, \vec{0}).
\] 
The spillover effect measures the difference in potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed. This effect can differ for either treated or control units as the magnitude or even the nature of spillovers might differ between treated and untreated units. That is $\tau_{i, \text{spill}}(1)$ does not necessarily equal $\tau_{i, \text{spill}}(0)$. We can then average over treated/control units to form average spillover effects: 
\[
    \tau_{\text{spill}}(D) \equiv \expec{Y_{i1}(D, h(\vec{D}, i)) - Y_{i1}(D, \vec{0}) \ \vert \ D_i = D},
\]
where the expectation is over individuals and hence over different exposures. This will give us the average spillover effect among \emph{all} treated/control units regardless if they receive any spillover effects. It is often also of interest to estimate the average spillover effects on subsets of units (e.g. all units experiencing non-zero exposure). Estimation of spillover effects will be discussed in Section \ref{sec:spill}.

With spillover effects formally defined, the difference between the proposed estimands become more clear by the following algebraic identity:
\begin{align*}
    &\overbrace{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i))}^{\text{Switching Effect}} = \\
    &\quad\quad \underbrace{\underbrace{Y_{i1}(1, 0) - Y_{i1}(0,0)}_{\text{Direct Effect}} \ + \ \underbrace{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, 0)}_{\text{Spillover on Treated}}}_{\text{Total Effect}} \ - \ \underbrace{(Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0,0))}_{\text{Spillover on Control}} 
\end{align*}

>>>>

Using this potential outcome framework, I define the different possible treatment/spillover effects of interest and the relative advantage and interpretation of each. First, there is the `switching effect' which is the relevant parameter for local policy makers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''. It is difficult to estimate the switching effect without parametric assumptions. The reason for this is that the magnitude of the switching effect potentially depends on the treatment status of a unit's neighbors. For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities versus the case where a close neighbor already has constructed one. Therefore, switching effects are defined seperately for each level of exposure and estimation of a switching effect requires knowledge of which units experience the same level of exposure. While the switching effect is not identified nonparametrically in general, there is one effect that is identified under mild assumptions. This effect is the `direct effect' of treatment which represents the switching effect for units with zero exposure to other treatment. That is, what are the effects of turning on a unit's treatment if this were the \emph{only} unit to be treated in their area.

Second, there is the `total effect' which is the relevant parameter for national policy makers who want to answer ``What is the average effect of implementing the entire treatment regime?''. This treatment effect summarizes what were the effects of going from the world with no treatment to the entire vector of treatment status. This effect comes from two sources: the direct effect and the average spillover effect from other treated units. Unlike the switching effect, the total effect effect is nonparametrically identified under a mild assumption that spillovers are `local' in that spillovers are only experienced within a certain distance from treatment.

This paper shows that the difference-in-differences esitmator is a biased estimate for the total effect because of spillover effects on control units. The intuition is that untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend. When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated units' change in outcomes. Hence, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect. For example, if nearby control units also benefit from treatment, then researchers would underestimate the effects on the treated. If a researcher is interested in the direct effect, there is an additional source of bias since changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of `close' units. The spillover onto other treated units is averaged into the treated units' change in outcomes. Therefore the bias on the direct effect estimate is the same sign as the sign of the spillover.

This paper then defines conditions under which each treatment effect is nonparametrically identified. I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences of treatment which requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the spillover effects. The other two treatment effects considered are able to be identfified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature which holds in the case where spillover effects are only experienced by units within a certain distance of treated units. This would hold in the case where individuals can travel to access treatment. This could fail in the case of large general equilibrium shocks that cause units far away to be affected by treatment (e.g. San Francisco being affected by shocks to New York economy).

Under the assumption that spillovers are local, I show a common adjustment of including an indicator for being affected by spillovers will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers. In my decomposition of the difference-in-differences estimate, the bias term for the total effect is the \textit{average} spillover effects onto control units. An indicator variable for control units affected by spillover can remove this bias. When estimating the direct effect, a second indicator variable for treated units affected by spillovers is included to remove the second source of bias. Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space. The only assumption required is selecting the maximum distance from treated units spillovers can occur.\footnote{Since treatment effects typically decay over distance, even if the maximum distance is not large enough, most of the bias will still be removed. On the other hand, making the maximum distance too large, will increase the variance in the estimates as there are fewer remaining control units to identify the parallel counterfactual unit.}

The modified difference-in-differences framework with an added spillover indicator provides a theoretically poor estimate of average spillover effects as it averages over all units with the indicator equal to 1 which can include units that are unaffected by spillovers. The above method can be improved by creating a set of distance bins from treated units (e.g. being 0-20 miles, 20-40 miles, 40-60 miles from treated unit) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers. In some cases, the bins can be determined in a data driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single large indicator, this estimator still consistently estimates the treatment effect of interest. This estimator has the added benefit that each indicator will estimate the average spillover effect on treated/control units within that distance range which provides a more complete picture of which units are affected by treatment and at what magnitude.

@@

I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework in two ways. \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}. My paper is the first to consider identification in terms of general potential outcomes. Other papers derive results for specific spillover mappings and if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs. The literatuere has focused on estimating the total effect, so I contribute by discussing alternative treatment effect estimates and identification results. Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.

This paper relates to a broad literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work. See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.}

There are two main strands of this literature. First, there is a large literature on estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers. Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares units in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects. This allows standard difference-in-differences estimation of both the total effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters). However, in many settings distinct clusters are not plausible, e.g. counties near the border of a state can effect eachother. My proposed estimator generalizes this method by using control units are unaffected by treatment without requiring a notion of clusters.

There is a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster in experimental settings (\citet{Savje_Aronow_Hudgens_2021}, \citet{Vazquez-Bare_2019}, and \citet{Hu_Li_Wager_2021}). Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings. I also contribute in this literature by thinking about different definitions of treatment effects and their identification in non-experimental settings.

@@

This section will present a potential outcome framework that formalizes spatial spillovers. The goal of this exercise is to formalize treatment effects which are no longer uniquely defined in settings with spillovers. Following the canonical difference-in-differences framework, I observe a panel of units for periods $t \in \{0,1\}$ and treatment turns on between periods for some of the units.\footnote{This can be extended to multiple periods by replacing $Y_{i0}$ and $Y_{i1}$ throughout with pre- and post- sample averages of $Y_{it}$. This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Let $D_{i}$ be an indicator equal to one if unit $i$ is treated and therefore treatment status is defined as $D_{it} = D_{i} * \one_{t = 1}$.

@@

Potential outcomes, denoted $Y_{it}(D_i, h_i(\vec{D}))$, are a function of unit $i$'s own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments. The non-negative scalar- or vector-valued function $h_i(\vec{D})$ is referred to as an `exposure mapping'. This setup follows \citet{Vazquez-Bare_2019} who studies identification of spillover effects under an experimental setting.\footnote{Note that throughout, expectations and inference are conditional on the vector of exposure mappings. In design-based settings, the distribution of exposure mappings is known so expectations can be taken without conditioning on the vector of exposure mappings. See \citet{Savje_Aronow_Hudgens_2021} for discussion estimation and inference when the treatment design is known.}

The exposure mapping formalizes the SUTVA violation by summarizing the intensity at which unit $i$ is affected by spillovers. Without any restrictions on the exposure mapping, nonparametric identification of treatment effects will be impossible. The main assumption for identification, as will be formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = \vec{0}$ . In the world of no spillovers, that is $h_i(\vec{D}) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.

@@

\begin{example}
    $h_i(\vec{D})$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure which tells the distance unit $i$ is from unit $j$.  In this case \begin{equation}\label{eq:h_within}
        h_i(\vec{D}) = \max_{j \neq i} D_j * \one_{ d(i,j) < \bar{d}}
    \end{equation}
    This exposure mapping is a realistic specification when it is assumed that spillover effects do not decay over distance until $\bar{d}$ and the intensity of spillovers does not depend on the number of neighboring units treated. For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}. In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library. The benefits of access to a neighboring town library does not depend on whether people can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.  
\end{example}

\begin{example}
    Second, $h_i(\vec{D})$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
        h_i(\vec{D}) = \sum_{j \neq i} D_j * \one_{d(i,j) < \bar{d}}.
    \end{equation}
    This exposure mapping is no longer binary, so the intensity of spillovers is additive in the number of nearby units treated. In the context of wholesale store openings, this exposure mapping captures the additive nature of agglomeration economies. As more nearby counties receive new stores, the force of agglomeration and therefore the spillover effect increases (e.g. \citet{Basker_2005}).
\end{example}

\begin{example}
    Last, $h_i(\vec{D})$ is a spatial decay function where exposure decreases with distance. In this case, spillover intensity is the sum across all treated observations' decay term, i.e. \begin{equation}\label{eq:h_decay}
        h_i(\vec{D}) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
    \end{equation} 
    This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units. This creates problems with inference because it implies potential correlation between all units' error terms. For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed that spillover effects decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using a non-linear least squares routine. In the literature on R\&D investment, for example, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure. This specification features exponential decay over distance which captures the theoretical insight that research spending in closer locations has a larger effect than further away spending.
\end{example}

@@

In setups without spillovers, treatment effects for an individual unit is well defined as $\tau_i \equiv Y_{i1}(1) - Y_{i1}(0)$, i.e. the effect of turning on treatment for a unit, and the above two assumptions would lead to identification of the average effect by the traditional difference-in-differences estimator. In the presence of spillovers, there are multiple treatment effects that can be defined in this setting. This subsection will define them and discuss their relative advantages/disadvantages.

The natural analogue to the above treatment effect which I will label the `switching effect' is:
\[
    \tau_{i, switch}(h_i(\vec{D})) \equiv Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})).
\] 
This is the effect of changing only unit $i$'s treatment status while keeping their exposure to spillovers constant. This treatment effect is policy relevant as it summarizes what would happen if a `local' policy makers decide to enact the policy for unit $i$ (implicity keeping $h$ constant).\footnote{This is what \citet{Savje_Aronow_Hudgens_2021} call the `assignment-conditional unit-level treatment effect'.} It is important to note that the switching effect can depend on the level of exposure. For instance, consider the construction of libraries in towns. The effect of library construction in a town that is far away from any other library (exposure of $\vec{0}$) can be different than a town that is very close to a neighboring town's library (large exposure), hence the dependence of $\tau_{i, switch}$ on $h_i(\vec{D})$. Since the size of the switching effect depends on a units exposure level, we will consider an average switching effect at each value of exposure, 
\[
    \tau_{\text{switch}}(\vec{h}) \equiv \condexpec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D}))}{D_i = 1, h_i(\vec{D}) = h}.
\]

% Work by \citet{Savje_Aronow_Hudgens_2021} suggests averaging the switching effect over exposure levels,
%\[ 
%    \tau_{\text{avg,switch}} \equiv \expec{\tau_{i, switch}(h_i(\vec{D})) \vert D_i = 1}.
%\] 
%This estimand averages the switching effect over all treated units and hence average over the distribution of exposure. Any given unit $i$ trying to understand the effect of switching on a policy can't use this parameter as it averages over exposures different than theirs. More, this parameter can not be identified without further assumptions as the distribution of exposure mappings is not necessarily the same for control units as treated units.\footnote{\citet{Savje_Aronow_Hudgens_2021} discuss conditions on the distribution of exposure mappings that can lead to asymptotic identification of the average switching effect. However it relies on design-based assumptions that do not apply here.}

There is a particular switching effect at zero exposure that I call the `direct effect' of treatment, 
\[
    \tau_{\text{direct}} \equiv \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, h_i(\vec{D}) = \vec{0}} = \tau_{\text{switch}}(\vec{0}),
\] 
which measures the average effect of being treated \emph{among unexposed treated units}. Specifying this particular switching effect will prove useful when discussing identification as it requires fewer assumptions than switching effects at other exposure levels. As discussed above, this is not necessarily a policy-relevant parameter for every unit if the switching effect has different magnitudes at different levels of exposure.

The second policy-relevant parameter is the `total effect of treatment': 
\[
    \tau_{\text{total}} \equiv \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}.
\] 
As opposed to the switching effect, which keeps exposure constant, the total effect looks at turning on treatment \emph{and} going from zero exposure to $h_i(\vec{D})$ simultaneously. This can be thought of as going from the world with a \emph{complete} absence of treatment, $\vec{0}$ to the current treatment vector $\vec{D}$. This treatment effect is helpful for `national' policy makers in order to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.

To better understand how the above treatment effects are connected, it will be useful to formalize a unit's `spillover effect' as:
\[
    \tau_{i, \text{spill}}(D_i, h_i(\vec{D})) \equiv Y_{i1}(D_i, h_i(\vec{D})) - Y_{i1}(D_i, \vec{0}).
\] 
The spillover effect measures the difference in potential outcomes between being exposed at intensity $h_i(\vec{D})$ and not being exposed. This effect can differ for either treated or control units as the magnitude or even the nature of spillovers might differ between treated and untreated units. That is $\tau_{i, \text{spill}}(1, h_i(\vec{D}))$ does not necessarily equal $\tau_{i, \text{spill}}(0, h_i(\vec{D}))$. We can then average over treated/control units to form average spillover effects: 
\[
    \tau_{\text{spill}}(D) \equiv \expec{Y_{i1}(D, h_i(\vec{D})) - Y_{i1}(D, \vec{0}) \ \vert \ D_i = D},
\]
where the expectation is over individuals and hence over different exposures. This will give us the average spillover effect among \emph{all} treated/control units regardless if they experience any spillover effects. It is often also of interest to estimate the average spillover effects on subsets of units (e.g. all units experiencing non-zero exposure). Estimation of spillover effects will be discussed in Section \ref{sec:spill}.

With spillover effects formally defined, the difference between the proposed estimands become more clear by the following algebraic identity:
\begin{align*}
    &\overbrace{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D}))}^{\text{Switching Effect}} = \\
    &\quad\quad \underbrace{\underbrace{Y_{i1}(1, 0) - Y_{i1}(0,0)}_{\text{Direct Effect}} \ + \ \underbrace{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0)}_{\text{Spillover on Treated}}}_{\text{Total Effect}} \ - \ \underbrace{(Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0,0))}_{\text{Spillover on Control}} 
\end{align*}
